hbm_paper_results

### 2023-12-20 paper_results.Rmd
fixed ratio file read-in

---
title: "ohbm_results"
output: html_document
date: '2023-11-12'
---

@@

```{r}
ratio_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_ratio"
raw_files <- list.files(path = ratio_data_path, pattern = "_pred.csv", full.names = TRUE)

@@

    # Add a "Source_File" column with the file name
    data <- data %>%
      mutate(Source_File = as.factor(basename(file))) %>%
      mutate(dataset = gsub("_data|_raw.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df_list <- c(df_list, list(data))
    assign("ratio_sites_list", df_list)
}
length(ratio_sites_list)
```

@@

Plot boxplots to compare across prop.
```{r}
ratio_diffs.df <- bind_rows(ratio_diffs) %>% 
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(perm, dataset) %>%
  dplyr::summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  dplyr::select(-ends_with(".z")) %>% #drop z-score cols
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

>>>>

---
title: "hbm_paper_results"
output: html_document
date: '2023-11-12'
---

@@

## Load Data

Read in centile/z-score errors

```{r}
ratio_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_ratio"
raw_files <- list.files(path = ratio_data_path, pattern = "_diffs.csv", full.names = TRUE)

df_list <- list() #new empty list
for (file in raw_files) {
  print(paste("reading file", file))
  # Read each CSV file
    data <- fread(file)

    data <- data %>%
     mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df_list[[file]] <- as.data.frame(data)
    assign("ratio_list", df_list)
}
length(ratio_list)
```

Read in subject-wise summary stats

```{r}
raw_files <- list.files(path = ratio_data_path, pattern = "_subj_pred.csv", full.names = TRUE)

@@

    data <- data %>%
      mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df_list <- c(df_list, list(data))
    assign("ratio_subj_list", df_list)
}
length(ratio_subj_list)
ratio_subj.df <- bind_rows(ratio_subj_list)
```

@@

Plot boxplots to compare across prop.
```{r}
# ratio_diffs.df <- bind_rows(ratio_diffs) %>% 
#   mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
#   group_by(perm, dataset) %>%
#   dplyr::summarize(across(starts_with("abs.diff_"), mean)) %>%
#   ungroup() %>%
#   dplyr::select(-ends_with(".z")) %>% #drop z-score cols
#   pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
#   mutate(pheno_cat = as.factor(case_when(
#       pheno %in% vol_list_global ~ "Global Volume",
#       pheno %in% vol_list_regions ~ "Regional Volume",
#       pheno %in% sa_list ~ "Regional SA",
#       pheno %in% ct_list ~ "Regional CT",
#       TRUE ~ NA_character_)),
#       label = sub("_[^_]*_", "_", pheno))

ratio_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff * 100) %>%
  ggplot() +
    geom_boxplot(aes(x=prop, y=mean_cent_abs.diff, fill=dataset)) +
  labs(y= "Magnitude Centile Error", x = "M:F Ratio in Site B") +
  ggtitle("Within-feature mean magnitude of error in centile scores across ComBat \nconfigurations as sex imbalance changes")
```
